---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4) 
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# `bind_rows()` and `bind_cols()`

---
# The `happy` data frame

.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# Split `happy` by row

```{r echo = TRUE}
happy_row_one <- happy %>% 
                  slice(1:2)
happy_row_two <- happy %>% 
                  slice(3:5)
```
--
`happy_row_one`  
```{r echo = FALSE}
happy_row_one
```
--
`happy_row_two`
```{r echo = FALSE}
happy_row_two
```
---
# Recreate `happy` using `bind_rows()`

.panelset[
```{r panelset = TRUE}
bind_rows(happy_row_one, happy_row_two)
```
]
---
# Order matters!

.panelset[
```{r panelset = TRUE}
bind_rows(happy_row_two, happy_row_one)
```
]
---
# Keep track of original data frames

.panelset[
```{r panelset = TRUE}
bind_rows(happy_row_one, happy_row_two, .id = "original_df")
```
]
---
# `bind_rows()` with unequal columns

.panelset[
```{r panelset = TRUE}
happy_row_two_cut <- happy_row_two %>% 
                      select(!social_support)
happy_row_two_cut
```
]
---
# `bind_rows()` with unequal columns

.panelset[
```{r panelset = TRUE}
bind_rows(happy_row_one, happy_row_two_cut)
```
]
---
# Split `happy` by column

```{r echo = TRUE}
happy_col_one <- happy %>% 
                  select(1:2)
happy_col_two <- happy %>% 
                  select(3:4)
```
--
.pull-left[
`happy_col_one`  
```{r echo = FALSE}
happy_col_one
```
]
--
.pull-right[
`happy_col_two`
```{r echo = FALSE}
happy_col_two
```
]
---
# Recreate `happy` using `bind_cols()`

.panelset[
```{r panelset = TRUE}
bind_cols(happy_col_one, happy_col_two)
```
]
---
# `bind_cols()` with unequal rows

.panelset[
```{r panelset = TRUE}
happy_col_two_cut <- happy_col_two %>% 
                        slice(1:4)
happy_col_two_cut
```
]
---
# `bind_cols()` with unequal rows

```{r echo = TRUE, eval = FALSE}
bind_cols(happy_col_one, happy_col_two_cut)
```

`Error in `bind_cols()`:`  
`! Can't recycle `..1` (size 5) to match `..2` (size 4).`  
---
