---
title: "Welcome to Tidybiology"
author:
- name: Matthew Hirschey
  affiliation: Duke University
  affiliation_url: https://duke.edu
- name: Akshay Bareja
date: "`r Sys.Date()`"
description: |
  R and data science for biologists
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome)
```


```{r links, fig.width = 10, fig.height = 10}
# from - https://stackoverflow.com/questions/48506712/kable-kableextra-cells-with-hyperlinks
# and - https://stackoverflow.com/questions/53549662/how-can-i-add-a-fontawesome-icon-to-a-table-in-rmarkdown

links <- c("https://bespokds.netlify.app/xaringan_dplyr/#1", "https://bespokds.netlify.app/xaringan_joins/#1",
"https://bespokds.netlify.app/xaringan_advanced_dplyr/#1")

df <- tribble(
  ~Class, ~Slides, ~Recording, ~Exercise,
  "Dplyr", paste0("<a href=\"", links[1], "\">", as.character(fa("tv")), "</a>"), as.character(fa("video")), as.character(fa("list")),
  "Joins", paste0("<a href=\"", links[2], "\">", as.character(fa("tv")), "</a>"), as.character(fa("video")), as.character(fa("list")),
  "Advanced Dplyr", paste0("<a href=\"", links[3], "\">", as.character(fa("tv")), "</a>"), as.character(fa("video")), as.character(fa("list"))
)

df %>% 
  kable("html", escape = FALSE, table.attr = "style='width:100%;'") %>%
  kable_styling(bootstrap_options = c("hover"))
```
\

+ [World Happiness Report EDA](exercise_happy/)

\

## Useful Resources

+ [R for Data Science](https://r4ds.had.co.nz)

+ [Exploratory Data Analysis & Visualization](https://edav.info/index.html)

+ [dplyr guide](https://dplyr.tidyverse.org)

+ [ggplot2 guide](https://ggplot2.tidyverse.org)

+ [From Data to Viz](https://www.data-to-viz.com)

+ [10 Minute Markdown Tutorial](https://commonmark.org/help/tutorial/)

+ [Past Projects](https://github.com/matthewhirschey/tidybiology-final_project/tree/master/2019_fall)

+ [bespokeDS YouTube channel](https://www.youtube.com/channel/UCstAS6IpgYgZ9Cvcag_YlCQ)


<aside> The R and Tidyverse online communities are very active, helpful, and welcoming. One of the best ways to learn new things is to follow the #rstats hashtag on Twitter. </aside>


\

## Acknowledgments {.appendix}

This website was modelled on a wonderful Distill website made by [Alison Hill & Desirée De Leon](https://github.com/rstudio-education/teaching-in-production/blob/master/index.Rmd)