---
title: "Welcome to Tidybiology"
author:
- name: Matthew Hirschey
  affiliation: Duke University
  affiliation_url: https://duke.edu
- name: Allie Mills
- name: Akshay Bareja
date: "`r Sys.Date()`"
description: |
  R and data science for biologists
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(fontawesome) # to see all options, run - fa_metadata()$icon_names %>% as_tibble() %>% View()
library(ggiraph)
```

\
```{r subway, fig.width = 10, fig.height = 10}
# crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
# 
# crimes$onclick <- sprintf("window.open(\"%s%s\")",
#   "http://en.wikipedia.org/wiki/", as.character(crimes$state) )
# 
# gg_crime <- ggplot(crimes, aes(x = Murder, y = Assault, color = UrbanPop )) + 
#   geom_point_interactive(
#     aes(data_id = state, tooltip = state, onclick = onclick ), size = 3 ) + 
#   scale_colour_gradient(low = "#999999", high = "#FF3333")
# 
# girafe(ggobj = gg_crime)

subway <- tribble(
  ~station, ~x, ~y, ~onclick, ~type, 
  "Intro to Data Science (tutorial)", 0, 1, 'window.open("https://akshay-bareja.shinyapps.io/ds_intro_track/")', "tutorial",
  "Intro to Data Science (video)", 0, 0.99, 'window.open("https://youtu.be/TnPlET9mk0s")', "video",
  "Intro to Data Science (tutorial)", 0, 0.98, 'window.open("https://akshay-bareja.shinyapps.io/ds_intro_track/")', "tutorial",
  "Intro to Data Science (video)", 0, 0.97, 'window.open("https://youtu.be/TnPlET9mk0s")', "video",
  "Intro to Dplyr (tutorial)", 0.2, 1, 'window.open("https://bespokds.netlify.app/xaringan_intro_to_dplyr/#1")', "tutorial",
  "Intro to Dplyr (video)", 0.2, 0.99, 'window.open("https://youtu.be/W3D-JSPExXo")', "video",
  "Intro to Pandas (tutorial)", 0.2, 0.75, '', "tutorial",
  "Intro Pandas (video)", 0.2, 0.74, '', "video",
  "Selecting Variables Using Dplyr (tutorial)", 0.4, 1, 'window.open("https://bespokds.netlify.app/xaringan_select/#1")', "tutorial",
  "Selecting Variables Using Dplyr (video)", 0.4, 0.99, 'window.open("https://youtu.be/vDgP7J1qMCI")', "video",
  "Selecting Variables Using Pandas (tutorial)", 0.4, 0.75, '', "tutorial",
  "Selecting Variables Using Pandas (video)", 0.4, 0.74, '', "video"
)

gg_subway <- ggplot(subway, aes(x = x, y = y)) +
               # tracks
               geom_segment(x = 0, xend = 0.2, y = 1, yend = 1, size = 5, colour = "blue") +
               geom_segment(x = 0, xend = 0.2, y = 0.99, yend = 0.99, size = 5, colour = "red") +
               geom_curve(x = 0, xend = 0.2, y = 0.98, yend = 0.75, size = 5, colour = "orange",
                          curvature = 0.05) +
               geom_curve(x = 0, xend = 0.2, y = 0.97, yend = 0.74, size = 5, colour = "darkgreen",
                          curvature = 0.05) +
               geom_segment(x = 0.2, xend = 0.2, y = 0.99, yend = 0.75, linetype = 2) +
               geom_segment(x = 0.2, xend = 0.4, y = 1, yend = 1, size = 5, colour = "blue") +
               geom_segment(x = 0.2, xend = 0.4, y = 0.99, yend = 0.99, size = 5, colour = "red") +
               geom_segment(x = 0.2, xend = 0.4, y = 0.75, yend = 0.75, size = 5, colour = "orange") +
               geom_segment(x = 0.2, xend = 0.4, y = 0.74, yend = 0.74, size = 5, colour = "darkgreen") +
               geom_segment(x = 0.4, xend = 0.4, y = 0.99, yend = 0.75, linetype = 2) +
               # stations
               geom_point(colour = "black", size = 2.5, stroke = 2) +
               geom_point_interactive(aes(tooltip = station, onclick = onclick), size = 1.9, colour = "white") +
               # track legend
               annotate("segment",
                        x = 0.05, xend = 0.1,
                        y = 1.05, yend = 1.05,
                        size = 1,
                        colour = "blue") +
               annotate("segment",
                        x = 0.05, xend = 0.1,
                        y = 1.03, yend = 1.03,
                        size = 1,
                        colour = "red") +
               annotate("text", 
                        label = "R track (tutorial)",
                        x = 0.135, y = 1.05,
                        size = 3,
                        fontface = "bold") +
               annotate("text",
                        label = "R track (video)",
                        x = 0.131, y = 1.03,
                        size = 3,
                        fontface = "bold") +
               annotate("segment",
                        x = 0.25, xend = 0.3,
                        y = 1.05, yend = 1.05,
                        size = 1,
                        colour = "orange") +
               annotate("segment",
                        x = 0.25, xend = 0.3,
                        y = 1.03, yend = 1.03,
                        size = 1,
                        colour = "darkgreen") +
               annotate("text", 
                        label = "Python track (tutorial)",
                        x = 0.347, y = 1.05,
                        size = 3,
                        fontface = "bold") +
               annotate("text",
                        label = "Python track (video)",
                        x = 0.345, y = 1.03,
                        size = 3,
                        fontface = "bold") +
               theme_void()

girafe(ggobj = gg_subway,
       height_svg = 3)
```

\
```{r links, fig.width = 10, fig.height = 10}
# from - https://stackoverflow.com/questions/48506712/kable-kableextra-cells-with-hyperlinks
# and - https://stackoverflow.com/questions/53549662/how-can-i-add-a-fontawesome-icon-to-a-table-in-rmarkdown

links <- c("https://bespokds.netlify.app/xaringan_intro_to_dplyr/#1", "https://bespokds.netlify.app/xaringan_select/#1",
"https://bespokds.netlify.app/xaringan_filter/#1",
"https://bespokds.netlify.app/xaringan_arrange/#1",
"https://bespokds.netlify.app/xaringan_mutate/#1",
"https://bespokds.netlify.app/xaringan_joins/#1",
"https://bespokds.netlify.app/xaringan_saving/#1",
"https://bespokds.netlify.app/xaringan_group_by_summarise/#1",
"https://bespokds.netlify.app/xaringan_filtering_joins/#1",
"https://bespokds.netlify.app/xaringan_helper_functions/#1",
"https://bespokds.netlify.app/xaringan_slice/#1",
"https://bespokds.netlify.app/xaringan_unite_separate/#1",
"https://bespokds.netlify.app/xaringan_pivot/#1",
"https://bespokds.netlify.app/xaringan_if_else/#1",
"https://bespokds.netlify.app/xaringan_case_when/#1",
"https://bespokds.netlify.app/xaringan_colwise/#1",
"https://bespokds.netlify.app/xaringan_rowwise/#1")

df <- tribble(
  ~Concept, ~Slides, ~Recording, ~Exercise,
  "Getting to Know Your Data", paste0("<a href=\"", links[1], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/W3D-JSPExXo", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Selecting Variables", paste0("<a href=\"", links[2], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/vDgP7J1qMCI", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Filtering Observations", paste0("<a href=\"", links[3], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/KWs8VNeWlbE", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Arranging Your Data", paste0("<a href=\"", links[4], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/BN9-zPuM-2g", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Adding New Columns", paste0("<a href=\"", links[5], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/stNOP4B1aGE", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Mutating Joins", paste0("<a href=\"", links[6], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/kLgZYO3tcYA", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Saving Your Work", paste0("<a href=\"", links[7], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "https://youtu.be/thw78gmuvM4", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Group By and Summarise", paste0("<a href=\"", links[8], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Filtering Joins", paste0("<a href=\"", links[9], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Selection Helpers", paste0("<a href=\"", links[10], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
   "Slice", paste0("<a href=\"", links[11], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Unite and Separate", paste0("<a href=\"", links[12], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Pivoting", paste0("<a href=\"", links[13], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "If/else", paste0("<a href=\"", links[14], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
   "case_when()", paste0("<a href=\"", links[15], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
  "Column-wise operations", paste0("<a href=\"", links[16], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard")),
   "Row-wise operations", paste0("<a href=\"", links[17], "\">", as.character(fa("laptop")), "</a>"), paste0("<a href=\"", "", "\">", as.character(fa("youtube-square")), "</a>"), as.character(fa("clipboard"))
)

df %>%
  kable("html", escape = FALSE, table.attr = "style='width:100%;'", align = 'c') %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>%
  #row_spec(row = 1:nrow(df), color = "white", background = "#90ee90") %>%# can start at 0 (to include header)
  column_spec(1, color = "darkblue") %>%
  column_spec(2, color = "black") %>%
  column_spec(3, color = "red") %>%
  column_spec(4, color = "brown")
```
\
```{r tracks, fig.width = 10, fig.height = 10}
links_two <- c("https://akshay-bareja.shinyapps.io/ds_intro_track/")

df_two <- tribble(
  ~Track, ~Tutorial, 
  "Introduction to Data Science", paste0("<a href=\"", links_two[1], "\">", as.character(fa("road")), "</a>"),
  "Exploratory Data Analysis", paste0("<a href=\"", "", "\">", as.character(fa("road")), "</a>"),
  "Making Plots", paste0("<a href=\"", "", "\">", as.character(fa("road")), "</a>"),
)

df_two %>%
  kable("html", escape = FALSE, table.attr = "style='width:100%;'", align = 'c') %>%
  kable_styling(bootstrap_options = c("hover", "condensed", "responsive")) %>%
  #row_spec(row = 1:nrow(df), color = "white", background = "#90ee90") %>%# can start at 0 (to include header)
  column_spec(1, color = "darkblue") %>%
  column_spec(2, color = "black") 
```


\

## Useful Resources

+ [R for Data Science](https://r4ds.had.co.nz)

+ [Exploratory Data Analysis & Visualization](https://edav.info/index.html)

+ [dplyr guide](https://dplyr.tidyverse.org)

+ [ggplot2 guide](https://ggplot2.tidyverse.org)

+ [From Data to Viz](https://www.data-to-viz.com)

+ [10 Minute Markdown Tutorial](https://commonmark.org/help/tutorial/)

+ [Past Projects](https://github.com/matthewhirschey/tidybiology-final_project/tree/master/2019_fall)

+ [bespokeDS YouTube channel](https://www.youtube.com/channel/UCstAS6IpgYgZ9Cvcag_YlCQ)


<aside> The R and Tidyverse online communities are very active, helpful, and welcoming. One of the best ways to learn new things is to follow the #rstats hashtag on Twitter. </aside>


\

## Acknowledgments {.appendix}

This website was modelled on a wonderful Distill website made by [Alison Hill & Desirée De Leon](https://github.com/rstudio-education/teaching-in-production/blob/master/index.Rmd)