---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4) 
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# If/else

---
# The `happy` data frame

.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# The if statement
--
```{r eval = FALSE}
if(condition){
  do this
}
```
---
# Example if statement

.panelset[
```{r panelset = TRUE}
if(7 > 5){
  print("is greater than 5")
}
```
]
--
.panelset[
```{r panelset = TRUE}
if(3 > 5){
  print("is greater than 5")
}
```
]
---
# if/else

```{r eval = FALSE}
if(condition){
  do A
} else {
  do B
}
```

---
# if/else

.panelset[
```{r panelset = TRUE}
if(7 > 5){
  print("is greater than 5")
} else {
  print("is less than 5")
}
```
]
---
# Applying if/else to `happy` data frame

.center[
```{r echo = FALSE}
happy_if <- happy %>% 
              mutate(in_europe = if_else(country_name == "Spain", TRUE, FALSE))

happy_if %>% 
  kbl %>% 
  kable_styling()
```
]
---
# Applying if/else to a vector

```{r eval = FALSE}
if(happy$country_name == "Spain"){
  print(TRUE)
} else {
  print(FALSE)
}
```
--
This won't work!
---
# Write a for loop?

.panelset[
```{r panelset = TRUE}
for(i in 1:length(happy$country_name)){
  if(happy$country_name[i] == "Spain"){
    print(TRUE)
  } else {
    print(FALSE)
  }
}
```
]
---
# Vectorized `ifelse()` 

.panelset[
```{r panelset = TRUE}
ifelse(happy$country_name == "Spain", TRUE, FALSE)
```
]  

--
```{r eval = FALSE}
ifelse(condition, Do A, Do B)
```
---
# Using `ifelse()` to modify a data frame

.panelset[
```{r panelset = TRUE}
happy %>% 
  mutate(in_europe = ifelse(country_name == "Spain", TRUE, FALSE))
```
]
---
# `if_else()` from the Dplyr package

.panelset[
```{r panelset = TRUE}
ifelse(happy$country_name == "Spain", TRUE, "No")
```
]  

--
```{r eval = FALSE}
if_else(happy$country_name == "Spain", TRUE, "No")
```

**Error** in `if_else()`:  
! `false` must be a logical vector, not a character vector.
---
