---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
happy_full <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/world-happiness-report-2021.csv") %>% clean_names() %>% rename(region = regional_indicator)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# Advanced `filter()`

---
# The `happy` data frame

.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# Simple example

Keep countries that have a `gdp` greater than 9 that are **NOT** Panama  
--
.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# Simple example

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(gdp > 9,
         country_name != "Panama")
```
]
---
# Table of Relational Operators

.center[
```{r echo = FALSE}
tribble(~Operator, ~Description,
        "==", "equals",
        "!=", "does not equal",
        ">", "greater than",
        "<", "less than",
        ">=", "greater than or equal to",
        "<=", "less than or equal to") %>% 
  kbl %>% 
  kable_styling()
```
]
---
# The `|` ("or") Operator

Keep countries that have a `gdp` less than 9 or greater than 10 
--
.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# The `|` Operator

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(gdp < 9|gdp > 10)
```
]
---
# The `!` Operator

*Discard* countries that have a `gdp` less than 9 
--

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(!gdp < 9)
```
]
---
# The `!` Operator

*Discard* countries that have a `gdp` less than 9 or greater than 10   

--
  
**WRONG!!!**  

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(!gdp < 9|gdp > 10)
```
]
---
# Operator Precedence

`!` precedes `|` 

--

Operator Syntax and Precedence - https://stat.ethz.ch/R-manual/R-devel/library/base/html/Syntax.html  

--
  
```{r eval = FALSE, echo = TRUE}
happy %>% 
  filter(!gdp < 9|gdp > 10)
```

--
  
**IS THE SAME AS**  
```{r eval = FALSE, echo = TRUE}
happy %>% 
  filter(gdp >= 9|gdp > 10)
```
---
# Operator Precedence 

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(!(gdp < 9|gdp > 10))
```
]
---
# Filter`%in%`g

Choose rows that correspond to Iraq, Panama, and Maldives  
--
.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(country_name == "Iraq"|
         country_name == "Panama"|
         country_name == "Maldives")
```
]
---
# Filter`%in%`g

**Note!!**
--
```{r echo = TRUE, eval = FALSE}
happy %>% 
  filter(country_name == "Iraq"|"Panama"|"Maldives")
```
--
Error in `filter()`:  
! Problem while computing `..1 = country_name == ("Iraq" | "Panama" | "Maldives")`.  
Caused by error in `"Iraq" | "Panama"`:  
! operations are possible only for numeric, logical or complex types  
---
# Filter`%in%`g

Use the `%in%` operator!  
--
.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(country_name %in% c("Iraq", "Panama", "Maldives"))
```
]
---
# Not `%in%`

Choose countries that are NOT Iraq, Panama, or Maldives 
--
.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(!country_name %in% c("Iraq", "Panama", "Maldives"))
```
]
