---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
happy_full <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/world-happiness-report-2021.csv") %>% clean_names() %>% rename(region = regional_indicator)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# `between()` and `near()`

---
# The `happy` data frame

.center[
```{r echo = FALSE}
happy %>% 
  kbl %>% 
  kable_styling()
```
]
---
# `between()`

Choose countries that have a `ladder_score` between (and including) 4.5 and 6.2
--
.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(ladder_score >= 4.5,
         ladder_score <= 6.2)
```
]
---
# `between()`

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(between(ladder_score, 4.5, 6.2))
```
]
---
# `near()`

Choose countries that have a `ladder_score` equal to 6 +/- 0.5
--
.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(between(ladder_score, 5.5, 6.5))
```
]
---
# `near()`

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(near(ladder_score, 6, tol = 0.5))
```
]
---
# `near()`

Choose countries that have a `ladder_score` equal to the mean `ladder_score` +/- standard deviation of `ladder_score` 

--

`https://suzan.rbind.io/2018/02/dplyr-tutorial-3/`  
--

.panelset[
```{r panelset = TRUE}
happy %>% 
  filter(near(ladder_score, mean(ladder_score), 
              tol = sd(ladder_score)))
```
]
---