---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include = FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(fig.width = 6, fig.height = 4) 
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
happy_full <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/world-happiness-report-2021.csv") %>% clean_names() %>% rename(region = regional_indicator)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# Selection Helpers

---
# Helper functions

A collection of functions that work especially well with `select()`

--

Includes `starts_with()`, `ends_with()`, `contains()`, `matches()`, and `everything()`
---
# The `happy_full` data frame

.center[
```{r echo = FALSE}
happy_full %>% 
  glimpse()
```
]
---
# `starts_with()`

Select all columns that begin with "explained_by"  
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(starts_with("explained_by"))
```
]
---
# `ends_with()`

Select all columns that end with the word "choices"  
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(ends_with("choices"))
```
]

---
# `contains()`

Select all columns that contain the word "log"  
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(contains("log"))
```
]
---
# `matches()`

Select all columns that *either* begin with word "explained" or end with the word "score"
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(contains("^explained|score$"))
```
]
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(matches("^explained|score$"))
```
]
---
# `everything()`

Re-order the data frame so that the first column is `ladder_score`
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  select(ladder_score, everything())
```
]
---
# `relocate()`

*NOTE: SHOW HOW THIS WORKS + HOW IT WORKS WITH HELPER FUNCTIONS*