---
title: Intro to Data Science using R
author: Akshay Bareja (Center for Computational Thinking)  
date: '2021-02-11'
output:
  ioslides_presentation:
    widescreen: yes
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(knitr)
library(here)
library(twitterwidget)
library(rlang)
library(ggrepel)
library(viridis)
library(gghighlight)
library(patchwork)
library(readxl)
library(lubridate)
knitr::opts_chunk$set(echo = FALSE, 
                      fig.align="center")
```

```{r load, include = FALSE, warning = FALSE, message = FALSE}
cauti_data <- read_csv("https://raw.githubusercontent.com/BAREJAA/cct_datasets/main/Staci%20Reynolds/cauti_data.csv?token=ALRLU72WC356M4XECRK35ATAB4526")
cauti_details <- read_csv("https://raw.githubusercontent.com/BAREJAA/cct_datasets/main/Staci%20Reynolds/cauti_details.csv?token=ALRLU7ZZ7DDFZMVCXZUKIUDAB46CA")

cauti_data$Month <- as.Date(cauti_data$Month)

cauti_data %>% 
  mutate(rate = `Number of CAUTIs`/`Foley Days` * 1000) %>% 
  mutate(mean = mean(rate, na.rm = TRUE)) %>% 
  mutate(sd = sd(rate, na.rm = TRUE)) %>% 
  mutate(ucl = mean + (3*sd),
         lcl = mean - (3*sd)) -> cauti_updated
```

## Doctors make decisions based on symptoms 
```{r intro, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://source.unsplash.com/701-FJcjLAQ/500x500"
knitr::include_graphics(url)
```
<font size = "1">Photo by [National Cancer Institute on Unsplash](https://unsplash.com/@nci)</font>

## New digital healthcare era introduces new decision-making challenges {.build}
**Volume**  
- Data collection & storage allows access to huge amounts of medical information  
  
**Ubiquity**  
- Data are available anywhere across geography, social, and economic classes   
  
**Latency**  
- Technology facilitates no delay in access to data    
  
## How do you make better health care decisions? {.build}
**Data-driven** decision making!  
  
```{r hierarchy, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://upload.wikimedia.org/wikipedia/commons/0/06/DIKW_Pyramid.svg"
knitr::include_graphics(url)
```
<font size = "1">https://en.wikipedia.org/wiki/DIKW_pyramid</font>
  
## Emerging field of Data Science
```{r venn1, echo=FALSE, fig.cap="", out.height= '100%'}
url <- "https://images.squarespace-cdn.com/content/v1/5150aec6e4b0e340ec52710a/1364352051365-HZAS3CLBF7ABLE3F5OBY/ke17ZwdGBToddI8pDm48kB2M2-8_3EzuSSXvzQBRsa1Zw-zPPgdn4jUwVcJE1ZvWQUxwkmyExglNqGp0IvTJZUJFbgE-7XRK3dMEBRBhUpxPe_8B-x4gq2tfVez1FwLYYZXud0o-3jV-FAs7tmkMHY-a7GzQZKbHRGZboWC-fOc/Data_Science_VD.png?format=1500w"
knitr::include_graphics(url)
```
<font size = "1">http://drewconway.com/zia/2013/3/26/the-data-science-venn-diagram</font>

## Venn Diagram of Data Science v2.0
```{r venn2, echo=FALSE, fig.cap="", out.height= '100%'}
url <- "https://3.bp.blogspot.com/-bvQxcwfqATQ/V-E_uTBc4VI/AAAAAAAAMGQ/Qa1Ntef-rs0E-mWx5pkVu-CPlREdvD0TwCLcB/s1600/VennDiagram2.png"
knitr::include_graphics(url)
```
<font size = "1">Joel Grus via KDnuggets</font>

## Overall goal is Knowledge Generation
```{r knowledge, echo=FALSE, fig.cap="", out.height = '100%'}
url <- "https://upload.wikimedia.org/wikipedia/commons/0/06/DIKW_Pyramid.svg"
knitr::include_graphics(url)
```
<font size = "1">https://en.wikipedia.org/wiki/DIKW_pyramid</font>

## Several Approaches to Knowledge Generation {.build}
- New tools allow data interrogation more easily than ever before 

```{r approaches, echo=FALSE}
tweet <- twitterwidget('1125268670324695041')
```
<center>`r tweet`</center>

## World's most popular programming languages
```{r popular, echo = FALSE}
excel <- tibble(
  name = c("Excel", "Java", "C", "C++", "Python"), 
  num = c(100000000, 9000000, 6000000, 4000000, 3000000)
)
excel_plot <- ggplot(excel) +
  geom_col(aes(x = fct_rev(fct_reorder(name, num)), y = num), fill = "navy") +
  labs(x = "", y = "Number of Users (Million)") +
  scale_y_continuous(labels = c("0", "25", "50", "75", "100")) +
  theme_minimal()
excel_plot
#need to add source
```

## R or Excel? {.build}
- Whichever works best for you!  

## R - pros {.build}
- Free  
- Open-source  
- Reproducible  
- Transparent 

## R - cons {.build}
- None :)  
- (slight) learning curve  

# R <br> language

## R is a language
```{r language, echo=FALSE, fig.cap=""}
url <- "https://source.unsplash.com/ZzWsHbu2y80/256x455"
knitr::include_graphics(url)
```
<font size = "1">Photo by Hannah Wright on Unsplash</font>

## R has values
- 1
- "North Carolina"
- "2020-04-08"

## R has objects
- A name without quotes  
- Assigned using `<-` (looks like an arrow pointing left)  
- Can be a value, object, or function result  

## Try assigning an object 
1. Assign an object; **remember, no quotes on name**  
`name <- 4`  
  
2. Return that object by typing its name  
`name`  
  
Try this in the code chunk below, then hit "Run Code"  

```{r my_first_object, exercise=TRUE}

```

## R has functions
- A name without quotes  
- Followed by () to run the function  
- Optional arguements: values, objects, or function results  
- `round(x, digits = 3)`

Try this in the code chunk below, then hit "Run Code"  

```{r my_first_fun, exercise=TRUE}
round(pi, digits = 3)

```

## Which of these are numbers?

```{r num_quiz, echo=FALSE}
question("Which of these are numbers?",
  answer("1", correct = TRUE),
  answer('"1"', message = "Because it has quotes, it is an string"),
  answer('"one"', message = "Because it has quotes, it is an string"),
  answer("one",  message = "R recognizes this as an object"), 
  allow_retry = TRUE, 
  random_answer_order = TRUE
)
```

## Which of these will work?
Suppose `one <- 1`
```{r one_quiz, echo=FALSE}
question("Which of these will work?",
  answer("log(1)", correct = TRUE),
  answer('log("1")', message = "You cannot log transform a word (string)"),
  answer('log("one")', message = "You cannot log transform a word (string)"),
  answer("log(one)", correct = TRUE), 
  allow_retry = TRUE, 
  random_answer_order = TRUE
)
```
Try it for yourself!  
  
```{r scratchpad, exercise=TRUE}
one <- 1
```

## Data are stored in tables and dataframes
Data stored in a dataframe are conceptually equivalent to a spreadsheet with rows and columns  

## Tidyverse 
Tidyverse is one suite of tools for data science  


## Exploratory Data Analysis
```{r r4ds, echo=FALSE, fig.cap="", out.width='66%'}
url <- "https://github.com/hadley/r4ds/raw/master/diagrams/data-science.png"
knitr::include_graphics(url)
```

## Tidyverse Basic Principles
**IMPORT** (readr):  
- `read_csv()`  
- `read_delim()`  
  
**TIDY & TRANSFORM** (dplyr):  
- `mutate()` adds new variables that are functions of existing variables  
- `select()` picks variables based on their names.  
- `filter()` picks cases based on their values.  
- `summarise()` reduces multiple values down to a single summary.  
- `arrange()` changes the ordering of the rows.  
  
**VISUALISE** (ggplot): creating graphics, based on ‘The Grammar of Graphics’  
- `aes()`  
- `geom_x()` + layers   
  
**MODEL** (broom):   
- `tidy()`, `glance()`, `augment()`  

----
```{r pipe, echo=FALSE, fig.cap="", out.width='77%'}
url <- "https://s3-us-west-2.amazonaws.com/collections.lacma.org-images/remote_images/ma-150089-WEB.jpg"
knitr::include_graphics(url)
```

## `magrittr` package
```{r magrittr, echo=FALSE, fig.cap="", out.width='40%'}
url <- "https://github.com/tidyverse/magrittr/raw/master/man/figures/logo.png"
knitr::include_graphics(url)
```

## `magrittr` package
`magrittr` package by Stefan Milton Bache developed the concept of the pipe, which is used heavily in the `tidyverse`  
  
  
```{r magrittr2, echo=FALSE, fig.cap="", out.width='40%'}
url <- "https://github.com/tidyverse/magrittr/raw/master/vignettes/magrittr.jpg"
knitr::include_graphics(url)
```
<br>  
<center><font size = "10">"and then"</font></center>

## The Pipe {.build}
  The “pipe” is a sequence of functions, that are sequentially applied to an object  
```{r wakeup, echo=TRUE, eval=FALSE}
wakeup(self) %>%
  put_on("clothes") %>%
  eat("breakfast") %>%
  go(to = "work")
```
  
  Alternative nested code:  
```{r wakeup_nested, echo=TRUE, eval=FALSE}
go(eat(put_on(wakeup(self), "clothes"), "breakfast"), to = "work")
```

## The Pipe (Quiz I)
What does this code do? 
  
```{r wakeup_quiz, echo=TRUE, eval=FALSE}
wakeup(self) %>%
  put_on("clothes") %>%
  eat("breakfast") %>%
  fmk() %>% 
  go(to = "work")
```
  
## The Pipe (Quiz II)
What does this code do? 
  
```{r wakeup_quiz2, echo=TRUE, eval=FALSE}
morning_routine <- wakeup(self) %>%
  put_on("clothes") %>%
  eat("breakfast") %>%
  fmk() %>% 
  go(to = "work")
```

# EDA <br> Getting to know your data  
## Datasets  

- For this class, we will use three datasets -  `cauti_data`, `cauti_updated`, and `cauti_details`   

## Inspecting your dataframe: dimensions

Use the `dim()` function to see how many rows (observations) and columns (variables) are in `cauti_data`

`dim(cauti_data)` 
  
Enter your function here:  
```{r dim_exercise, exercise=TRUE}

```

## Inspecting your dataframe: glimpse

Use the `glimpse()` function to see what kinds of variables the `cauti_data` dataset contains   
  
`glimpse(cauti_data)`  
  
Enter your function here:  
```{r glimpse_exercise, exercise=TRUE}

```

## Basic Data Types in R {.build}

R has different data types -

**character** - `"a"`, `"tidyverse"`  

**numeric** - `2`, `11.5`  

**integer** - `2L` (the `L` tells R to store this as an integer)  

**logical** - `TRUE`, `FALSE`  

**complex** - `1+4i`  

(**raw**)

You will also come across the **double** datatype. It is the same as **numeric**

**factor**. A **factor** is a collection of *ordered* character variables

## Basic Data Types in R

In addition to the `glimpse()` function, you can use the `class()` function to determine the data type of a specific column

`class(cauti_data$Month)`

```{r class, echo = FALSE, warning = FALSE}
class(cauti_data$Month)
```

## Introducing `dplyr` {.build}
  
dplyr is a package that contains a suite of functions that allow you to easily manipulate a dataset  
  
Some of the things you can do are -  
  
- select rows and columns that match specific criteria  
  
- create new variables (columns)  
  
- obtain summary statistics on individual groups within your datasets  
  
The main verbs we will cover are `select()`, `filter()`, `arrange()`, `mutate()`, and `summarise()`. These all combine naturally with `group_by()` which allows you to perform any operation "by group"  

## `cauti_details` dataset

How do look into `cauti_details`?  

```{r glimpse_cauti_details, exercise=TRUE}

```

## `select()` specific columns from your dataset {.build}
The most basic `select()` is one where you comma separate a list of columns you want included

For example, if you only want to select the `Age` and `Gender` columns, run the following code chunk

`cauti_details %>%`   
    `select(Age, Gender)`
    
```{r select_exercise, exercise=TRUE}

```

## `select()` {.build}

If you want to select all columns *except* `Age`, run the following

`cauti_details %>%`   
    `select(-Age)`

```{r selectnot_exercise, exercise=TRUE}

```

## `select()` {.build}

Finally, you can provide a range of columns to return two columns and everything in between. For example

`cauti_details %>%`   
    `select(Age:Diagnosis)`
    
```{r selectrange_exercise, exercise=TRUE}

```

## `filter()` rows based on certain condition(s) {.build}

The `filter()` verb evalutes a logical statement, and if a row meets the condition of this statement (i.e. is true) then it gets chosen (or "filtered").  
  
  
**All other rows are discarded**  

## `filter()` {.build}

Filtering can be performed on **categorical** data

`cauti_details %>%`   
    `filter(Diagnosis == "ICH")`

```{r filter_exercise, exercise=TRUE}

```

## `filter()` {.build}

Filtering can also be performed on **numeric** data

For example, if you wanted to choose `Age` with a value greater than 35, you would run the following. 

`cauti_details %>%`   
    `filter(Age > 35)` 

```{r filter_exercise2, exercise=TRUE}

```

## `filter()` {.build}

To filter on multiple conditions, you can write a sequence of `filter()` commands

`cauti_details %>%`   
    `filter(Diagnosis == "ICH") %>%`
    `filter(Age > 35)` 

```{r filter_exercise3, exercise=TRUE}

```

## `filter()` {.build}

To avoid writing multiple `filter()` commands, multiple logical statements can be put inside a single `filter()` command, separated by commas

`cauti_details %>%`   
    `filter(Diagnosis == "ICH",`
            `Age > 35)`

```{r filter_exercise4, exercise=TRUE}

```
## `arrange()` sorts rows {.build}

The input for arrange is one or many columns, and `arrange()` sorts the rows in ascending order i.e. from smallest to largest

For example, to sort rows from smallest to largest `Age`, run the following

`cauti_details %>%`   
    `arrange(Age)`

```{r arrange_exercise, exercise=TRUE}

```

## `arrange()` {.build}

To reverse this order, use the `desc()` function within `arrange()`

`cauti_details %>%`   
    `arrange(desc(Age))` 

```{r arrange_exercise2, exercise=TRUE}

```

## `mutate()` {.build}

The `mutate()` verb, unlike the ones covered so far, creates new variable(s) i.e. new column(s). For example

`cauti_data %>%`   
    `mutate(rate = `Number of CAUTIs`/`Foley Days` * 100)` 
  
The code chunk above divides `Number of CAUTIs` by `Foley Days` for each row, and populates a new column called `rate` with these results
  
## Try `mutate()` to make a new column
  
`cauti_data %>%`   
    `mutate(rate = `Number of CAUTIs`/`Foley Days` * 100)` 
  
```{r mutate_exercise, exercise=TRUE}

```

## `summarise()` and `summarize()` {.build}

`summarize()` is one of the key functions in `dplyr`. It produces a new dataframe that aggregates that values of a column based on a certain condition.  
  
For example, to calculate the mean `Age`, run the following

`cauti_details %>%`   
    `summarize(mean(Age))` 

```{r summarize_exercise, exercise=TRUE}

```

## `group_by()` {.build}

`group_by()` and `summarize()` are a powerful combination of functions to summarize by groups  
  
`cauti_details %>%`   
    `group_by(Gender) %>%`
    `summarize(mean(Age))` 
  
```{r groupby_exercise, exercise=TRUE}

```

## EDA using `cauti_details`

`cauti_details %>%` 
  `group_by(Gender) %>%` 
  `count(Diagnosis) %>%` 
  `arrange(desc(n))`
  
```{r eda_one, exercise=TRUE}

```

## EDA using `cauti_details`

`cauti_details %>%` 
  `group_by(Gender) %>%` 
  `summarise(mean_foley = mean(`Foley Days`),`
            `mean_age = mean(Age))`
  
```{r eda_two, exercise=TRUE}

```

# Control charts using ggplot2

## Our goal

```{r control_chart, echo = FALSE, warning = FALSE}
cauti_updated %>% 
  ggplot(aes(Month, rate)) +
  geom_line() +
  geom_point() +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") +
  geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +
  geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed") +
  scale_x_date(date_breaks = "1 month") +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) 
```

## `cauti_updated` dataset

How do we take a look into `cauti_updated`?

```{r cauti_updated_glimpse, exercise=TRUE}

```

## Visualize Data with
```{r ggplot_logo, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="", out.height = '100%'}
url <- "https://github.com/tidyverse/ggplot2/raw/master/man/figures/logo.png"
knitr::include_graphics(url)
```
<font size = "1">[https://ggplot2.tidyverse.org](https://ggplot2.tidyverse.org)</font>

## Basics of a ggplot code {.build}

Below is an example of the most basic form of the ggplot code  
  
`ggplot(data = dataframe, mapping = aes(x, y)) +`   
  `geom()`  
  
Take a moment to look back at the code template.  You can see that in that code we assigned a `dataset` and the information we needed to `map` it to a type of plot

## Basics of a ggplot code {.build}

`ggplot(data = cauti_updated, mapping = aes(x = Month, y = rate)) +`  
    `geom_point()`  
  
```{r simple_plot, echo = FALSE, warning = FALSE}
ggplot(data = cauti_updated, mapping = aes(x = Month, y = rate)) + 
    geom_point()
```

## Basics of a ggplot code {.build}

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point()`  
  
```{r simple_plot_two, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point()
```

## Adding layers 

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line()`

```{r adding_layers, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line()
```

## Adding labels

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart")`   

## 
```{r adding_labels, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart")
```

## Adjusting x-axis 

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`    
    `geom_line() +`    
    `labs(x = "",` 
         `y = "Rate",`
         `title = "Control chart") +`  
    `scale_x_date(date_breaks = "1 month")`       

##
```{r adjusting_x_axis, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") 
```

## Highlighting key data points

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`
    `scale_x_date(date_breaks = "1 month") +`  
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red")`  

##
```{r highlighting_points, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red")
```

## Adding helpful lines

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`  
    `scale_x_date(date_breaks = "1 month") +`  
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red") +`  
    `geom_hline(aes(yintercept = mean), colour = "green")`  

##
```{r helpful_lines_one, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") 
```

## Adding helpful lines

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`
    `scale_x_date(date_breaks = "1 month") +`  
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red") +`  
    `geom_hline(aes(yintercept = mean), colour = "green") +`  
    `geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed")`  

##
```{r helpful_lines_two, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") +
  geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed")
```

## Adding helpful lines

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`   
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`  
    `scale_x_date(date_breaks = "1 month") +`  
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red") +`  
    `geom_hline(aes(yintercept = mean), colour = "green") +`  
    `geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +`  
    `geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed")`  

##
```{r helpful_lines_three, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") +
  geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +
  geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed")
```

## Changing the overall plot theme

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`
    `scale_x_date(date_breaks = "1 month") +`      
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red") +`  
    `geom_hline(aes(yintercept = mean), colour = "green") +`  
    `geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +`  
    `geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed") +`  
    `theme_bw()`

##
```{r plot_theme, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") +
  geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +
  geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed") +
  theme_bw()
```
 
## Adjusting axis text

`ggplot(cauti_updated, aes(x = Month, y = rate)) +`  
    `geom_point() +`  
    `geom_line() +`  
    `labs(x = "",`
         `y = "Rate",`
         `title = "Control chart") +`
    `scale_x_date(date_breaks = "1 month") +`  
    `geom_point(data = filter(cauti_updated, rate > mean), col = "red") +`  
    `geom_hline(aes(yintercept = mean), colour = "green") +`  
    `geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +`  
    `geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed") +`  
    `theme_bw() +`  
    `theme(axis.text.x = element_text(angle = 90))`  

##
```{r x_axis_text, echo = FALSE, warning = FALSE}
ggplot(cauti_updated, aes(x = Month, y = rate)) + 
    geom_point() +
    geom_line() +
  labs(x = "",
       y = "Rate",
       title = "Control chart") +
  scale_x_date(date_breaks = "1 month") +
  geom_point(data = filter(cauti_updated, rate > mean), col = "red") +
  geom_hline(aes(yintercept = mean), col = "green") +
  geom_hline(aes(yintercept = ucl), col = "blue", linetype = "dashed") +
  geom_hline(aes(yintercept = lcl), col = "orange", linetype = "dashed") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90))  
``` 
 
# Concluding Thoughts

## Data science enables {.build}
- Data science enables data-driven information gathering and hypothesis generation  
-- Scientific Research  
-- Reviews  
  
- Data science enables the ability to ask new types of questions  
  
- Process-centric, not necessarily question-centric  
  
- Making things computable makes them actionable at zero marginal cost.  
  
- Workflows save time, achieve reproducibility  

## Cheatsheet Resources
<a href="https://rstudio.com/resources/cheatsheets" target="_blank">Cheatsheets</a><br>

## Google Resources
<a href="https://google.com/" target="_blank">Google.com</a><br>

## R4DS Resources
<a href="https://r4ds.had.co.nz" target="_blank">R for Data Science</a><br>

## Acknowledgements {.build}
- Staci Reynolds, Ph.D.  
- Bradi Granger, Ph.D.  
- Matthew Hirschey, Ph.D.  
  
**Inspiration, ideas, packages, code**  
- R4DS (Garrett Grolemund and Hadley Wickham)  
- Mine Çetinkaya-Rundel (datasciencebox.org)  
- Chester Ismay and Albert Y. Kim (Modern Dive)  
- Garrett Grolemund  (Remastering the Tidyverse)  
- Tidyverse devs and community  
- Rstudio  

# Thank you
Any questions?
