---
title: "Tidybiology"
subtitle: "⚔<br/>Intro to Data Science Using R"
author: "Matthew Hirschey & Akshay Bareja"
institute: "Duke University"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(tidyverse)
library(kableExtra)
library(xaringanExtra)
library(janitor)
library(xaringanthemer)

happy <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/happy_small.csv")
happy_full <- read_csv("https://raw.githubusercontent.com/BAREJAA/website_for_john/master/datasets/world-happiness-report-2021.csv") %>% clean_names() %>% rename(region = regional_indicator)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#00539B",
  header_font_google = google_font("Adobe Caslon"),
  text_font_google   = google_font("Adobe Caslon", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r xaringanExtra-freezeframe, echo = FALSE, message = FALSE}
options(htmltools.dir.version = FALSE)
xaringanExtra::use_freezeframe()
```

```{r xaringanExtra-clipboard, echo=FALSE}
xaringanExtra::use_clipboard()
```

```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

---
class: center, middle

# `group_by() and summarize()` 

---
# `summarise()` and `summarize()`

`summarize()` is one of the key functions in `dplyr`. It produces a new dataframe that aggregates that values of a column based on a certain condition  

--
  
For example, to calculate the mean `ladder_score`, run the following  

--
.panelset[
```{r panelset = TRUE}
happy %>% 
  summarize(mean(ladder_score))
```
]
---
# `group_by()` 

`group_by()` and `summarize()` are a powerful combination of functions to summarize by groups 

--

To show off the power of this duo, let's take a look at the entire dataset - called `happy_full` - that contains additional columns, one of which is called `region`  

--

Let's take a look at this full dataset
  
```{r happy_full, echo = FALSE}
head(happy_full)
```
---

# `group_by()`

Let's again calculate the mean `ladder_score` but this time by region
--
.panelset[
```{r panelset = TRUE}
happy_full %>% 
  group_by(region) %>% 
  summarize(mean(ladder_score))
```
]